---
title: "Eating Out"
author: "Jaylen"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```



```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```
  
This bar graph shows that white people eat out more than both black and other people, however black and other people eat out at a similar number. 




```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
  
According to this numerical data white people eat out more than black or other people, however black and other people eat ut at a similar but rate but with a wider margin than the bar graph showed. 






```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```



